%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nikhill Rao}} & Email : \href{mailto:rnikhill@umich.edu}{rnikhill@umich.edu}\\
   \href{https://github.com/rnikhill}{https://github.com/rnikhill}& Mobile : 9062312643 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Bachelors of Science in Engeering, Computer Science}{Aug. 2013 -- April 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Thomson Reuters}{Ann Arbor, MI}
      {Software Engineer, 1040 State Tax}{June 2017 - Present}
      \resumeItemListStart
        \resumeItem{Ultratax CS}
          {Windows Desktop program used by professionals to prepare tax returns and generate electronic files. Maintained and enhanced several state tax products as the sole engineer for each product. Responsibilities included calculation logic, XML E-File generation and validation, 2-dimensional bar codes, and quality control. Handled regular, concurrent product releases and updates in a time-sensitive environment}
        \resumeItem{Onvio}
          {In-development cloud-based software suite for accountants and tax professionals. Migrated state tax products from desktop system into micro-services which were subsequently maintained}
      \resumeItemListEnd

    \resumeSubheading
      {Quantcast Corporation}{San Francisco, CA}
      {Software Engineer Intern, Developer Tools}{Jun 2015 - Aug 2015, Jan 2016 - Jun 2016}
      \resumeItemListStart
        \resumeItem{Ganglia Monitoring System}
          {Distributed, parallel system for monitoring and collecting metrics of
          high-performance clusters and grids. Developed extensions allowing cross-version compatibility and improve performance at scale}
        \resumeItem{Cloud Metrics and Monitoring}
            Extended Ganglia-based internal metric-collecting utility to easily specify alternate or multiple output collection platforms, simplifying process of evaluating and deploying alternative metrics system
        \resumeItem{Git Migration}
            Developed Python script to migrate entire organization’s Git repositories from Atlassian Stash to Github, with error handling,  logging, and migration of permissions.

      \resumeItemListEnd

    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Teaching Assistant}{Aug 2014 - April 2017}
      \resumeItemListStart
        \resumeItem{Instructional Aide - Data Structures and Algorithms}
          {Led weekly discussions, held office hours for student consultation, and developed course materials including programming projects, homework, labs, and exams}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{RoBob Ross}
      {Autonomous Robotics (EECS 467)  final project. Paints a representation of an input image using a robotic arm with a paintbrush. Used Python with openCV to generate stroke pattern from input image involving color reduction, contour-detection, and path-generation}
    \resumeSubItem{Style-Independent Image Recognition}
      {Machine Learning (EECS 445) final project: Attempted to train a convolutional neural network to recognize the content of images with different visual styles, using neural-style algorithm to generate training data.}
    \resumeSubItem{Multi-CPU Thread Library}
      {Operating Systems (EECS 482) Developed thread library with support for mutexes, condition variables, and simultaneous execution on multiple CPUs.}
	\resumeSubItem{Directed Study (EECS 399) Project}
	  {Reviewed and suggested extensions to Lego-Mindstorms based tutorial for the SOAR cognitive architecture/artificial intelligence platform}
	
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C++, Python, Scala, Typescript, Swift, SQL}
      \hfill
      \textbf{Technologies}{: AWS, AngularJS, Bash/Unix}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

